Chronic conditions and increased antibiotic consumption

### 2017-03-14 chronic-conditions/chronic-condition-drivers.Rmd
more lasso

```{r}
chronic_conditions %>% head(100) %>% write_tsv('tmp')
```

@@

```{r lasso}
library(glmnet)
lasso_x = usage_summary %>%
  select(age, is_female, AMI:HYPOTH) %>%
  mutate_at(vars(AMI:HYPOTH), function(x) if_else(x==3, 1L, 0L)) %>%
  as.matrix
lasso_y = usage_summary$n_claims
lasso_model = glmnet(lasso_x, lasso_y, family='poisson')
```

@@

multivariate_linear_res = usage_summary %>%
  lm(multivariate_formula, data=.) %>%
  tidy
```

```{r multivariate_poisson_model}
multivariate_poisson_res = usage_summary %>%
  glm(multivariate_formula, family='poisson', data=.) %>%
  tidy
```

@@

### Multivariate models

@@

#### Multivariate linear

I don't expect a linear model to work well, since the output is count data.

@@

#### Multivariate Poisson

This should be more accurate.

```{r cache=FALSE}
multivariate_poisson_res %>%
  mutate(pct.increase=round((exp(estimate)-1.0)*100)) %>%
  arrange(desc(pct.increase)) %>%
  kable
```

#### Lasso

I also performed a lasso regression with the Poisson model. I'm not sure how to display the results sensibly. I picked a value of $s$ that limited me to just a few nonzero model coefficients.

```{r cache=FALSE}
lasso_model %>%
  coef(s=0.25) %>%
  tidy %>%
  select(term=row, coefficient=value) %>%
  kable
```

>>>>

@@

```{r lasso}
library(glmnet)
require(doMC)
registerDoMC(cores=3)

lasso_x = usage_summary %>%
  select(age, is_female, AMI:HYPOTH) %>%
  as.matrix
lasso_y = usage_summary$n_claims

lasso_cv = cv.glmnet(lasso_x, lasso_y, parallel=TRUE, family='poisson')
#lasso_model = glmnet(lasso_x, lasso_y, family='poisson')
```

@@

multivariate_linear_res = usage_summary %>%
  lm(multivariate_formula, data=.) %>%
  tidy

# For multivariate Poisson:
# glm(multivariate_formula, family='poisson', data=.)
```

@@

### Multivariate linear model

@@

I don't expect a linear model to work well, since the output is count data, but doing a Poisson regression took a really long time.

@@

### Lasso

I also performed a lasso regression with the Poisson model. I started with 10-fold cross-validation to pick the $\lambda$.

```{r cache=FALSE}
plot(lasso_cv)
```

Although the error continues to fall with decreasing $\lambda$, it seems like there are diminishing returns after the first 8 or 10 variables are included.

```{r cache=FALSE}
lasso_df = lasso_cv$glmnet.fit %>%
  tidy %>%
  filter(estimate > 0) %>%
  group_by(step) %>%
  summarize(df=n() - 1)

lasso_cv$glmnet.fit %>%
  tidy %>%
  select(step, lambda, dev.ratio) %>%
  distinct() %>%
  left_join(lasso_df, by='step') %>%
  select(step, df, lambda) %>%
  mutate_at(vars(lambda), function(x) signif(x, digits=2)) %>%
  kable
```

It looks like this corresponds to $\lambda \sim 0.1$. For that value, the coefficients are:

```{r cache=FALSE}
lasso_cv %>%
  coef(s=0.1) %>%
  tidy %>%
  select(term=row, coefficient=value) %>%
  kable
```
